---
title: "Netflix Activity Dashboard"
date: 'Updated: `r Sys.Date()`'
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: paper
runtime: shiny
resource_files:
- input/NetflixViewingHistory_Metis.csv
- input/NetflixViewingHistory_Philip.csv
---

<style>                     
.navbar {
  background-color:#141414;
  border-color:white;
  opacity: 0.85;
}
.navbar-brand {
color:white!important;
}
</style>

<style>
.chart-title {  /* chart_title  */
   font-size: 18px;
   color: black;
</style>

<style>
.section.sidebar {
background-color:#A0A3A4;
border-color: #A0A3A4;
color: #000000! important;
}
</style>

<style>
.dropdown-menu {
    background-color: white;
}
</style>

```{r setup, include=FALSE}
# import packages
library(tidyverse)
library(gridExtra) # to plot multiple ggplot objects
library(scales)
library(lubridate)
library(readxl)
library(readr)
library(zoo)
library(reshape2)
library(kableExtra)
library(flexdashboard)
library(htmlwidgets)
library(DT)
library(shiny)
library(plotly)
library(treemap)
library(highcharter)
library(viridisLite)
library(data.table)
library(rvest)
library(treemapify)
library(bslib)
library(shinyWidgets)

# Import personal Netflix viewing data
# personal viewing data - exported directly from Netflix website
# specifies all xlsx files within our input folder
file_names <- list.files(
  path = "input", 
  pattern = "*.csv",
  full.names = TRUE)

# for loop to import multiple csv files from input folder directory
for (i in file_names){
  df <- read_csv((i))
  assign(substr(i, 7, nchar(i)) , df)
  rm(df)
}

# bind Metis' watch history & Philip's history into a single dataframe
NetflixViewingHistory_Metis.csv$User <- "Metis"
NetflixViewingHistory_Philip.csv$User <- "Philip"
binded_csv <- rbind(NetflixViewingHistory_Metis.csv, NetflixViewingHistory_Philip.csv)

# Manipulate binded_df 
# split title into 2 separate columns
manipulated_csv <- binded_csv %>% 
  separate(Title, into = c("Title", "Description"), sep = ":") %>% 
  filter(!is.na(Title)) %>% 
  mutate(Manipulated_Title = str_to_lower(Title)) %>% 
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, " ","-")) %>% 
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "!", "")) %>% 
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "’", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "'", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "&", "and")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "‘", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, ",", "")) %>%
  mutate(
    Type = case_when(
      is.na(Description) ~ "movie",
      TRUE ~ "tv-show"
    )
  ) %>% 
  select(-Description) %>% 
  mutate(web_scrape_URL = paste0("https://justwatch.com/us/",Type,"/",Manipulated_Title))

# Import Netflix data based on webscraped data
watched_movies_shows_vector <- as.vector(unique(manipulated_csv$web_scrape_URL))

# for loop to scrape all the movie data captured from the website;
# URL: https://www.justwatch.com/
for (i in 1:length(watched_movies_shows_vector)){
  justwatch_link <- watched_movies_shows_vector[i]
  justwatch_page <- try(read_html(justwatch_link), silent = TRUE)
  Title <- try(justwatch_page %>% html_nodes("h1") %>% html_text(), silent = TRUE)
  Genre <- try(justwatch_page %>% html_nodes(".detail-infos__value span") %>% html_text(), silent = TRUE)
  Runtime <- try(justwatch_page %>% html_nodes(".detail-infos:nth-child(4) .detail-infos__value") %>% html_text(), silent = TRUE)

  i_df <- try(data.frame(Title, Genre, Runtime, stringsAsFactors = FALSE) %>%
    mutate(Genre = str_replace_all(Genre, ",","")) %>%
    mutate(Genre = str_trim(Genre, side = c("both"))) %>%
    filter(Genre != "") %>%
    distinct(), silent = TRUE)

  if (!exists("justwatch_df")){
    justwatch_df <- i_df
  } else {
    justwatch_df <- rbind(justwatch_df, i_df)
  }
  rm(i_df)
  rm(justwatch_page)
}

Genres_vector <- as.vector(c("History", "Documentary", "Music & Musical", "Sport", "Horror",
                           "Reality TV", "Crime", "Myster & Thriller", "Fantasy", "Comedy",
                           "Western", "Animation", "Action & Adventure", "Science-Friction", "Romance", "Drama"))

justwatch_manipulated_df <- justwatch_df %>%
  filter(!str_detect(Title,"Error")) %>%
  filter(Genre %in% Genres_vector) %>%
  group_by(Title, Runtime) %>%
  summarise(Genre = paste0(Genre, collapse = ", ")) %>%
  ungroup() %>%
  mutate(Title = str_trim(Title, side = c("both"))) %>%
  mutate(Manipulated_Title = str_to_lower(Title)) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, " ","-")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "!", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "’", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "'", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "&", "and")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "‘", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, ",", "")) %>%
  mutate(Manipulated_Title = str_replace_all(Manipulated_Title, "ū", "u")) %>%
  select(-Title)

# Export justwatch_manipulated_df to csv file
write_csv(justwatch_manipulated_df, "output/justwatch_manipulated_df.csv")

# Import hard-coded df
# justwatch_manipulated_df <- read_csv("output/justwatch_manipulated_df_fixed.csv")

# left join justwatch_manipulated_df (web scraped) to personal activity data
df <- manipulated_csv %>% left_join(justwatch_manipulated_df, by = c("Manipulated_Title" = "Manipulated_Title")) 

# remove any rows w/ NA values
na.omit(df)  

# Separate runtime into 2 separate columns
manipulated_df <- df %>% 
  mutate(Year = year(Date)) %>% 
  mutate(MonthStartDate = as.Date(as.yearmon(Date, format = "%b%Y"), frac = 0)) %>% 
  relocate(Year, .after = Date) %>% 
  relocate(MonthStartDate, .after = Year) %>% 
  separate(Runtime, into=c("Hour", "Minute"), sep = " ") %>% 
  relocate(Genre, .before = Hour) %>% 
  mutate(Minute = case_when(is.na(Minute) & str_detect(Hour, "min") ~ Hour, TRUE ~ Minute)) %>% 
  mutate(Hour = case_when(str_detect(Hour, "min") ~ "0h", TRUE ~ Hour)) %>% 
  filter(Hour != "TV-MA") %>% 
  mutate(Hour = as.numeric(str_replace_all(Hour,"h", ""))) %>% 
  mutate(Minute = as.numeric(str_replace_all(Minute,"min", ""))) %>% 
  mutate(Total_Minutes = (Hour * 60) + Minute) %>% 
  mutate(Total_Hours = round(Total_Minutes / 60, 0)) %>% 
  mutate(Month = month(Date)) %>% 
  mutate(WeekDay = weekdays(Date)) %>% 
  mutate(Type = str_to_title(Type))

# remove individual monthly sales dataframes (for cleanliness)
rm(list=ls(pattern=".csv"))

# Color scale for this dashboard
color_scale <- c("#E50914", "#141414")
# color_scale <- c("#FFC1E7", "#7CDAE3")

metis_color <- color_scale[1]
philip_color <- color_scale[2]
both_color <- "#A0A3A4"

genre_split_df <- manipulated_df %>% 
  separate_rows(Genre, sep = ",") %>%
  mutate(Genre = str_trim(Genre, side = "both"))
```

column {.sidebar}
-----------------------------------------------------------------------
```{r}
# User
selectInput(
  inputId = "v_User",
  label = "User",
  choices = c("All", unique(manipulated_df$User)),
  selected = "All")

# Movie or TV-Show?
selectInput(
  inputId = "v_Type",
  label = "Movie/TV-Show",
  choices = c("All", unique(manipulated_df$Type)),
  selected = "All")

# Genre
selectInput(
  inputId = "v_Genre",
  label = "Genre",
  choices = c("All", unique(genre_split_df$Genre)),
  selected = "All")

# Date Range Slider
sliderInput(
  inputId = "v_DateRange",
  label = "Date Range",
  min = min(manipulated_df$Date),
  max = max(manipulated_df$Date),
  value = c(
    min(manipulated_df$Date),
    max(manipulated_df$Date)
  ),
  timeFormat="%Y-%m-%d"
)
```

Column {data-width=600}
-----------------------------------------------------------------------

### Watch Time (Hours)
```{r, fig.width = 18}
renderPlotly({
  manipulated_df %>% 
    filter(str_detect(User, if_else(input$v_User == "All", "", input$v_User))) %>%
    filter(str_detect(Type, if_else(input$v_Type == "All", "", input$v_Type))) %>%
    filter(str_detect(Genre, if_else(input$v_Genre == "All", "", input$v_Genre))) %>%
    filter(Date >= input$v_DateRange[1] & Date <= input$v_DateRange[2]) %>%
    group_by(User, MonthStartDate) %>% 
    summarise(`Watch Time (Hours)` = round(sum(Total_Minutes)/60,0)) %>% 
    ungroup() %>% 
    ggplot(aes(x = MonthStartDate, y = `Watch Time (Hours)`, fill = User)) +
    geom_bar(stat = 'identity') +
    theme_bw() +
    scale_x_date(date_labels="%Y-%m-%d", date_breaks = "1 month") +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) + # reduces the gap between y axis
    labs(
      x = "Month",
      y = "Watch Time (Hours)"
    ) +
    theme(axis.text.x = element_text(angle = 90)) +
    scale_fill_manual(values = c("Metis" = alpha(metis_color, 0.85), "Philip" = alpha(philip_color, 0.85)))
})

```

### Watch Time (Cumulative Hours)
```{r, fig.width = 18}
renderPlotly({
  manipulated_df %>% 
    filter(str_detect(User, if_else(input$v_User == "All", "", input$v_User))) %>%
    filter(str_detect(Type, if_else(input$v_Type == "All", "", input$v_Type))) %>%
    filter(str_detect(Genre, if_else(input$v_Genre == "All", "", input$v_Genre))) %>%
    filter(Date >= input$v_DateRange[1] & Date <= input$v_DateRange[2]) %>%
    group_by(User, MonthStartDate) %>% 
    summarise(`Watch Time (Hours)` = round(sum(Total_Minutes)/60,0)) %>% 
    ungroup() %>% 
    arrange(User, MonthStartDate) %>% 
    group_by(User) %>% 
    summarise(
      MonthStartDate,
      `Watch Time (Hours)`,
      `Cumulative Watch Time (Hours)` = cumsum(`Watch Time (Hours)`)
    ) %>% 
    ungroup() %>% 
    ggplot(aes(x = MonthStartDate, y = `Cumulative Watch Time (Hours)`, color = User)) +
    geom_point(size = 1, alpha = 0.85) +
    geom_line(size = 0.5, alpha = 0.85) +
    theme_bw() +
    scale_x_date(date_labels="%Y-%m-%d", date_breaks = "1 month") +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) + # reduces the gap between y axis
    labs(
      x = "Month",
      y = "Watch Time (Hours)"
    ) +
    theme(axis.text.x = element_text(angle = 90)) +
    scale_color_manual(values = c("Metis" = metis_color, "Philip" = philip_color))
})

```

Column {.tabset data-width=400}
-----------------------------------------------------------------------

### Weekday Activity
```{r, fig.width = 10}
renderPlotly({
  manipulated_df %>% 
    filter(str_detect(User, if_else(input$v_User == "All", "", input$v_User))) %>%
    filter(str_detect(Type, if_else(input$v_Type == "All", "", input$v_Type))) %>%
    filter(str_detect(Genre, if_else(input$v_Genre == "All", "", input$v_Genre))) %>%
    filter(Date >= input$v_DateRange[1] & Date <= input$v_DateRange[2]) %>%
    ggplot(aes(
      x = factor(WeekDay, levels = c(
        'Monday', 'Tuesday', 'Wednesday', 
        'Thursday', 'Friday', 'Saturday', 'Sunday')), 
      y = Total_Minutes,
      fill = User)) + 
    geom_boxplot(outlier.colour = NULL) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "", y = "Watch Time (Minutes)") +
    scale_fill_manual(values = c("Metis" = alpha(metis_color, 0.7), "Philip" = alpha(philip_color, 0.7))) +
    facet_wrap(~User, dir = "v") +
    theme(
      legend.position = "none",
      strip.background = element_rect(color="black", fill="white", size = 0.5, linetype = "solid"),
      strip.text.x = element_text(size = 12, color = "black", face = "bold"))
})
```

### Top Genres
```{r, fig.width = 10}
renderPlotly({
  plot_ly(
    data = genre_split_df %>%
            filter(str_detect(User, if_else(input$v_User == "All", "", input$v_User))) %>%
            filter(str_detect(Type, if_else(input$v_Type == "All", "", input$v_Type))) %>%
            filter(str_detect(Genre, if_else(input$v_Genre == "All", "", input$v_Genre))) %>%
            filter(Date >= input$v_DateRange[1] & Date <= input$v_DateRange[2]) %>%
            group_by(Genre) %>%
            summarise(`Watch Time (Hours)` = round(sum(Total_Minutes)/60,0)) %>%
            ungroup() %>%
            arrange(desc(`Watch Time (Hours)`)),
    type = "treemap",
    values = ~`Watch Time (Hours)`,
    parents = "Watch Time (Hours) by Genre: movies/shows may contain multiple genres",
    labels = ~Genre,
    domain = list(column = 0),
    textinfo = "label+value",
    marker = list(colorscale = 'Reds'))
})

```

### Top Movies/Shows
```{r, fig.width = 15}
renderPlotly({
  manipulated_df %>% 
    filter(str_detect(User, if_else(input$v_User == "All", "", input$v_User))) %>%
    filter(str_detect(Type, if_else(input$v_Type == "All", "", input$v_Type))) %>%
    filter(str_detect(Genre, if_else(input$v_Genre == "All", "", input$v_Genre))) %>%
    filter(Date >= input$v_DateRange[1] & Date <= input$v_DateRange[2]) %>%
    group_by(Title) %>% 
    mutate(ViewerCount = n_distinct(User)) %>% 
    ungroup() %>% 
    mutate(Viewer = case_when(ViewerCount > 1 ~ "Both", TRUE ~ User)) %>% 
    group_by(Viewer, Title, Type) %>% 
    summarise(`Watch Time (Hours)` = round(sum(Total_Minutes)/60,0)) %>% 
    arrange(Viewer, Type, desc(`Watch Time (Hours)`)) %>% 
    ungroup() %>% 
    group_by(Viewer, Type) %>%
    mutate(Rank = row_number()) %>% 
    filter(Rank <= 5) %>% 
    ggplot(aes(x = reorder(Title, `Watch Time (Hours)`), y = `Watch Time (Hours)`, fill = Viewer)) +
    geom_bar(stat = 'identity') +
    coord_flip() +
    theme_bw() +
    labs(x = "", y = "Watch Time (Hours)") +
    facet_wrap(~Viewer, scales = "free_y", dir = "v") +
    scale_fill_manual(values = c("Both" = both_color, "Metis" = alpha(metis_color, 0.85), "Philip" = alpha(philip_color, 0.85))) +
    scale_y_continuous(expand = expansion(mult = c(0, .1))) + # reduces the gap between y axis
    theme(
      legend.position = "none",
      strip.background = element_rect(color="black", fill="white", size = 0.5, linetype = "solid"),
      strip.text.x = element_text(size = 12, color = "black", face = "bold"))
})

```
